---
title: "Movies"
output: html_notebook
---

```{r setup}
# Packages ----
library(DBI)
library(tidyverse)
library(corrr)
library(dbplot)
library(tidypredict)
library(parsnip)
library(modeldb)

# Plot settings ----
old_theme <- theme_set(theme_bw())
```


# Intro
The movies dataset is available [from Kaggle](https://www.kaggle.com/danielgrijalvas/movies) and contains details about 6820 different movies. The following columns are included:

  + `budget`: the budget of a movie. Some movies don't have this, so it appears as 0
  + `company`: the production company
  + `country`: country of origin
  + `director`: the director
  + `genre`: main genre of the movie
  + `gross`: revenue of the movie
  + `name`: name of the movie
  + `rating`: rating of the movie (R, PG, etc.)
  + `released`: release date (YYYY-MM-DD)
  + `runtime`: duration of the movie
  + `score`: IMDb user rating
  + `star`: main actor/actress
  + `votes`: number of user votes
  + `writer`: writer of the movie
  + `year`: year of release
  
This data has been placed in a Teradata DB for further analysis.

# Connect
First, connect to the database. In this case, a DSN is being used.

```{r connection}
con <- dbConnect(
  odbc::odbc(),
  "Teradata"
)
```

Next, establish a connection to the specific movies table.
```{r movies}
movies_tbl <- tbl(con, "movies")
```

# Plotting
Use `dbplot` to plot data from the database
```{r dbplot}
dbplot_bar(movies_tbl, genre)
```

```{r}
db_compute_count(movies_tbl, genre) %>% 
  rename(n = 'n()') %>% 
  mutate(genre = fct_reorder(genre, -n, max)) %>% 
  ggplot(aes(x = genre, y = n)) +
  geom_col()
```

# Correlations
Use the `corrr` package to identify correlations in the movies dataset.
```{r correlation}
movies_sub <- movies_tbl %>% 
  select_if(is.numeric)

movies_cor <- correlate(movies_sub)
```

```{r ordered-correlation}
movies_cor %>% 
  shave() %>% 
  stretch() %>% 
  drop_na() %>% 
  arrange(desc(abs(r)))
```

```{r correlation-plot}
network_plot(movies_cor)
```

# Modeling
## modeldb
The [`modeldb` package](https://tidymodels.github.io/modeldb/) can be used to fit a model inside the database.

```{r modeldb-model}
db_model <- movies_tbl %>% 
  select(gross, budget, runtime) %>% 
  linear_regression_db(gross, auto_count = TRUE)

db_model
```
## tidypredict
Use the `tidypredict` package to run predictions against data in the database.

The [`tidypredict` package](https://tidymodels.github.io/tidypredict/) is used to run predictions inside a database. It does this by taking an R model and translating the object into appropriate SQL commands. The following models are supported:

  + Linear Regression
  + Generalized Linear Model
  + Random Forest
  + MARS models
  + XGBoost models
  + Cubist models
  + Tree models

Build simple linear model to predict movie gross

```{r local-model}
# Local copy of the data
movies_lcl <- collect(movies_tbl)

# Fit model
model <- linear_reg() %>% 
  set_engine("lm") %>% 
  fit(gross ~ budget + runtime + rating + genre + company, data = movies_lcl)

model
```

Use `tidypredict_to_column()` to generate predictions in the database
```{r tidypredict-in-db}
movies_tbl %>% 
  tidypredict_to_column(model) %>% 
  rename(local_fit = fit) %>% 
  tidypredict_to_column(as_parsed_model(db_model)) %>% 
  rename(remote_fit = fit) %>% 
  select(name, gross, local_fit, remote_fit) %>% 
  head(10)
```

SQL Model - this is how the model is translated to run inside the database
```{r tidypredict-sql}
tidypredict_sql(model, con)
```

Parse model
```{r tidypredict-parse}
parsed_model <- parse_model(model)
str(parsed_model)
```

# Disconnect
```{r disconnect}
dbDisconnect(con)
```




